\section{Introduction}



Vacuum polarization is a phenomenon in quantum electrodynamics (QED) by which the vacuum of a charged field polarizes when subject to external electric fields, effectively behaving like a dielectric with $\epsilon>0$. This mechanism was one of the first QED effects studied \cite{dirac_discussion_1934}, with consequences that followed closely \cite{uehling_polarization_1935,heisenberg_consequences_1936}. This mechanism has been already observed, e.g.~in corrections to atomic levels \cite{lamb_fine_1947} (cf. Ref.~\cite{mohr_qed_1998} for a review), while other effects e.g.~the Schwinger effect \cite{schwinger_gauge_1951} lay beyond current technological advances (cf. Ref.~\cite{fedotov_advances_2023}). 


Defining vacuum polarization  for generic backgrounds\footnote{And any other observable defined through the evaluation of products of fields or their derivatives at coinciding points.} is no easy task. Historically, \cite{dirac_discussion_1934} first defined it through the assumption that the short-distance behavior of the physically relevant states in the presence of strong background electric fields is the same as in their absence, only up to smooth coefficients. In modern bibliography, these states are called Hadamard, (cf Ref.~\cite{fewster_necessity_2013}), and they are particularly interesting in the context of quantum field theory on curved spacetimes, where the same idea is used to define observables necessary for the study of e.g.~perturbative interacting field theory or semiclassical gravity (cf.~\cite{hollands_local_2001,hollands_quantum_2015} for detailed discussions on the definition on such observables).

Semiclassical gravity, a possible first step towards a quantum theory of gravity, couples classical gravity  to the expectation value of the stress-energy tensor, which similarly as the vacuum polarization needs to be redefined. To our knowledge, only perturbative corrections to the metric have been studied  \cite{thompson_quantum-corrected_2024}. In this article we study, as a toy model, the effect of the backreaction of a charged scalar field to a background classical electric field in 1+1 dimensional Minkowski spacetime. This setup was already studied in  \cite{ambjorn_properties_1983}, where it was found that ignoring the backreaction of the scalar field leads to instabilities, and it claims that the inclusion thereof avoids them.
However, as pointed out in \cite{schlemmer_current_2015}, the expression used in \cite{ambjorn_properties_1983} for vacuum polarization $\rho$  cannot be derived from a manifestly gauge invariant prescription. \cite{wernersson_vacuum_2021} derives the correct expression for $\rho$, which has  qualitative disagreements with the one used in \cite{ambjorn_properties_1983}. 

This discussion motivates the following question, which we answer in the present paper: Given the difference in the prescriptions for $\rho$, does using the correct one avoid these instabilities? We will use the correct prescription described in \cite{wernersson_vacuum_2021} to implement an iterative method to study the effect of the backreaction of the scalar field. It has been found that this expression also alleviates the above mentioned instabilities.  

The layout of this article is as follows: Section 2 ...

\textbf{Maybe add?}: \cite{costeri_hadamard_2025} discusses hadamard states in the pressence of time-like boundaries.

This article summarizes and extends the results of the M.Sc. thesis of Santiago Sanz-Wuhl, written in 2025 at the Institut für Theoretische Physik, Universität Leipzig, under the supervision of Jochen Zahn.