\section{The iterative procedure}
\label{sec:The-iterative-procedure}

The effect of the backreaction of the scalar field to the background
electromagnetic field is studied by an iterative procedure. This procedure is
best described in the language of infinite dimensional fixed point problems. An external electric field given by $A_0$, displaces the charges inducing the vacuum polarization $\rho$ (cf. Eq.~\eqref{eq:vacuum-polarization-long}), which in itself induces a new electric potential (cf. Eq.~\eqref{eq:A0-general}). We look for the fixed points  $A_0$ of certain update function $f$
\begin{align}
    A_0 = f(A_0),
    \label{eq:fixed-point-problem}
\end{align}
where $f$ is the composition of all the steps described in the above sections. In summary, for a given potential $A_0$, 
\begin{enumerate}
    \item  the modes of the scalar field $\phi$ from Eq.~\eqref{eq:mode-equation} are calculated,
    \item  the corresponding vacuum polarization $\rho$ is calculated according to  Eq.~\eqref{eq:vacuum-polarization-long} and Sec.~\ref{sec:Computing-the-vacuum-polarization},
    \item  the corresponding potential $A_0$ is calculated following Eq.~\eqref{eq:A0-general} and returned. 
\end{enumerate}
The fixed points of $f$, denominated ``self-consistent solutions", are looked for by studying the limit $\lim_{\kappa\to \infty}A_{0,\lambda}^{\kappa}$, where 
\begin{align}
    A_{0,\lambda}^{\kappa + 1} = f(A_{0,\lambda}^{\kappa}) =
    f^{\kappa}\left(A_{0, \lambda}^{0} \right), \textrm{with } f^\kappa =
    \underbrace{f \circ ... \circ f}_{k \textrm{ times}}.
    \label{eq:self-consistent-limit}
\end{align}
If the limit $A_{0, \lambda}^{\infty}$ exists, it is given the name
self-consistent potential, as well as the corresponding self-consistent vacuum
polarization $\rho_{\lambda}^{\infty}$, field modes $\phi_{n,
\lambda}^{\infty}$ and mode energies $\omega_{n, \lambda}^{\infty}$.

For low enough $\lambda\ll \lambda_c$, the initial value of the sequence $A_{0,
\lambda}^0$  can be safely set to the external field approximation $A_{0,
\lambda}^0(z) = -\lambda \left(z- \frac{1}{2}\right).$ For bigger $\lambda$,
this potential is no longer a valid starting potential  as it might lead to
non-convergences in the sequence $ A_{0, \lambda}^{\kappa}$, as discussed in the Appendix
??\marginnote{Discuss the non-convergences of $A_{0, \lambda}$}. Due to the instabilities
of the external field approximation briefly discussed above, the use of this
approximation for $A_{0, \lambda}^{0}$, with a high enough $\lambda$-value,
also leads to complex $\omega_{n,\lambda}$. For higher $\lambda$-values,
$A_{0, \lambda}^{0}$ is instead set by an already calculated self-consistent
potential $A_{0, \lambda'}^{\infty}$ with $\lambda = \lambda' + \Delta
\lambda$, where $\Delta \lambda > 0$. Using this scheme, the
$\lambda$-parameter space is probed. 


At each iteration step $\kappa$, the update function $ f$ performs the
following calculations
\begin{subequations}
   \label{eq:iterative-procedure}
\begin{align}
    \frac{d {^2}\phi_{n, \lambda}^{\kappa}}{d {z^2}} {}  &= 
    -\left[ (\omega_{n, \lambda}^\kappa - \varepsilon A^{\kappa -1 }_{0, \lambda} )^2 
     - a^2 m^2\right] \phi_{n, \lambda}^{\kappa}, 
    \label{eq:mode-equation-iterative}
    \\
    \rho_\lambda^{\kappa} &= \lim_{\tau \to 0} \left[\sum_{n>0}^{} (\omega_{n,
        \lambda}^\kappa - \varepsilon A_{0, \lambda}^{\kappa-1} )\lvert \phi_{n,
        \lambda}^\kappa\rvert^2 e^{-i\omega^\kappa_{n, \lambda} \tau}
        +\sum_{n<0}^{} (\omega^{\kappa}_{n, \lambda} - \varepsilon
        A_{0, \lambda}^{\kappa-1}) \lvert \phi^\kappa_{n, \lambda}\rvert^2
    e^{i\omega^{\kappa}_{n, \lambda} \tau}\right] +
    \frac{\varepsilon^2}{\pi}
    A_{0, \lambda}^{\kappa-1} ,\\
    A^{\kappa }_{0, \lambda} &= c A_{0, \lambda}^{\kappa-1} + \left(1-c
        \right)\left[ -\lambda\left(z - \frac{1}{2} \right) -
            \int_{\frac{1}{2}}^{z} \int_{0}^{z'} \rho_\lambda^{\kappa}(z'') d z'' d
    z' \right] .
        \label{eq:A0-general-iterative}
\end{align}
\end{subequations}
Here, $c\in [0, 1]$ is introduced in order to ``relax" the procedure: For
$c=0$, the procedure is precisely the one used in~\cite[]{Ambjorn:1981xv}. For
$c$ close to 1, updates will only be corrections to the previous potential.
This avoids certain numerical instabilities as $\lambda   > \lambda_c$. 
Slower convergence schemes becomes increasingly relevant as $\lambda$ grows,
which makes the system more unstable.
%The mode subindices have been removed to avoid notation clutter.
%The iterative procedure is schematized in Fig.~\ref{fig:iterative-procedure},
%and it studies $\lim_{\kappa \to \infty} A_\lambda^\kappa $ for each $\lambda$.
%If the limit exists, it defines the self-consistent potential
%$A^{\infty}_\lambda$. Additionally, every other relevant quantity
%$\rho^\infty_\lambda, \omega_\lambda^{\infty}, \text{ and } \phi_\lambda
%^{\infty}$ also acquire the adjective ``self-consistent".

\input{Figures/iterativeLoop.tex}

%For a low $\lambda\ll \lambda_c$, the initial potential $A_\lambda^{0} = -\lambda
%\left(z-\frac{1}{2}\right)$ is given by the external field approximation. For
%higher values of $\lambda$, $A_\lambda^{0}$ is given by an already calculated
%self-consistent $A_{\lambda'}^{\infty}$, with $\lambda = \lambda' + \Delta
%\lambda$, for $\Delta \lambda > 0 $. 
